---
title: "HW_LiveSeesion4"
author: "Manisha Pendekar"
date: "February 7, 2018"
output: html_document
---
#1. Get the eighteenth dataset from FiveThirtyEight GitHub Data 
a. Install and load "FiveThirtyEight" package in R
```{r echo=TRUE}
#install.packages("fivethirtyeight")
library(fivethirtyeight)
```
b. Assign the eighteenth dataset to a dataframe object called "df" in R 

```{r echo=TRUE}
listofDs <- data(package = "fivethirtyeight")
items <- listofDs$results[, "Item"]
eighteenth <- items[18]
eighteenth
df <- college_recent_grads
#vignette("fivethirtyeight", package = "fivethirtyeight")
```
c. Here is the URL "http://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/" from command "vignette("fivethirtyeight", package = "fivethirtyeight")"
```{r echo=TRUE}
#vignette("fivethirtyeight", package = "fivethirtyeight")
```
d. Print the dimensions of the dataset contained in the "df" object
* Count of Rows and Columns the college_recent_grads dataset
```{r echo=FALSE}
dim(df)
```
#2. Data Summary of college_recent_grads
a. Write an R command that gives you the column names of the data frame.  Right after that, write one that counts the number of columns but not rows.  Hint: The number should match one of your numbers in Question 1d for dimensions.
```{r echo=TRUE}
# names of the columns in college_recent_grads dataset
names(df)
# count of columns in college_recent_grads dataset
ncol(df)
```
b. Generate a count of each unique major_category in the data frame.  I recommend using libraries to help.  I have demonstrated one briefly in live-session.  To be clear, this should look like a matrix or data frame containing the major_category and the frequency it occurs in the dataset.  Assign it to major_count.
```{r echo=TRUE}
# install dplyr library to get Tally funtion
#install.packages("dplyr")
library(dplyr)
major_count <- tally(group_by(df, major_category))
major_count
```
c. To make things easier to read, put par(las=2) before your plot to make the text perpendicular to the axis.  Make a barplot of major_count.  Make sure to label the title with something informative (check the vignette if you need), label the x and y axis, and make it any color other than grey.  Assign the major_category labels to their respective bar.  Flip the barplot horizontally so that bars extend to the right, not upward.  All of these options can be done in a single pass of barplot().
```{r echo=TRUE}
# Barplot of Major categories
par(las=2)
barplot(height = major_count$n, names.arg = major_count$major_category, xlab = "Frequency", horiz = TRUE, col = "green", main = "The frequencies of College Majors of recent graduate students")
```

d. Write the fivethirtyeight data to a csv file. Make sure that it does not have row labels.
```{r echo=TRUE}
# Write a CSV file containing college_recent_grads dataset
#write.csv(df, file = "C:\\Manisha\\DDS\\Week4RecentGrads.csv", row.names = FALSE)
#Post GitHub link to homework folder
```
# 3. My GitHub Account Folder link
