---
title: "Unit 5: Tidy Data"
author: "Manisha Pendekar"
date: "February 13, 2018"
output: html_document
---
#1. Data Munging 
a. Read the yob2016.txt and set column names
```{r echo=TRUE}
#########Q1a
df <- read.table(file = "C:\\Manisha\\DDS\\Week 5\\Class5Documents\\yob2016.txt", header = FALSE, sep = ";")
#dim(df)
head(df)
#str(df)
names(df) <-  c("Name", "Gender", "CountName")
```
b. Summary and Structure of df
```{r echo=TRUE}
str(df)
summary(df)
```
c. Display the misspelled record
```{r echo=TRUE}
df[grep("yyy$",df$Name),]
```
d. Remove the misspelled record and save the cleaned dataset in y2016
```{r echo=TRUE}
y2016 <- df[-grep("yyy$",df$Name),]
```
#2. Data Merging
a. Read the yob2015.txt and set column names
```{r echo=TRUE}
y2015 <- read.table(file = "C:\\Manisha\\DDS\\Week 5\\Class5Documents\\yob2015.txt", header = FALSE, sep = ",")
names(y2015) <-  c("Name", "Gender", "CountName")
```
b. Display the last ten rows in the dataframe.  Describe something you find interesting about these 10 rows
* The last 10 rows of this dataset have baby names which start with Z in 
alphabetically sorted order. These last 10 records shows the names given to baby-boys 
with each count of 5.
```{r echo=TRUE}
tail(y2015, 10)
#The last 10 rows of this dataset have baby names which start with Z in 
#alphabetically sorted order. These last 10 records shows the names given to #baby-boys with each count of 5.
```
c. Merge y2016 and y2015 and create a column final. There are no NA values in either of your amount of children rows after merging.
```{r echo=TRUE}
final <- merge(y2015, y2016, by = "Name")
### The following code will check whether there are any NA (na.fail returns the object
#if it does not contain any missing values, and signals an error otherwise.)
naCount <- na.fail(final$CountName.x)
naCount <- na.fail(final$CountName.y)

#head(final)
```
#3. Data Summary
a. Column Total which contains the amount of children in 2015 and 2016 together.  
```{r echo=TRUE}
final$Total<- rowSums(final[, c(3, 5)])
```
* In those two years combined, how many people were given popular names?
```{r echo=TRUE}
###In those two years combined, how many people were given popular names?
sum(final$Total)
```
b. Sort the data by Total.  What are the top 10 most popular names?
```{r echo=TRUE}
sortedFinal <-final[order(final$Total),]
tail(sortedFinal[[1]], 10)
```
c. Top 10 most popular girl names
```{r echo=TRUE}
girlNames <- final[final$Gender.y == "F",]
girlNames <- girlNames[order(girlNames$Total),]
top10girlNames <- tail(girlNames, 10)
top10girlNames[,1]
```
d. Write the Top 10 most popular girl names to .csv file with Totals
```{r echo=TRUE}
write.csv(top10girlNames[,c("Name","Total")], file="C:\\Manisha\\DDS\\top10girlNames.csv",row.names=FALSE)
```
4. Github Link
